Screen Time Review of Reviews Summary

### 2021-09-16 index.Rmd
Seperate meets vs doesn't meet credibility criteria

```{r, fig.cap=paste("Forest Plot for ", plots[[1]]$name," Outcomes"), fig.width=12, fig.height=10}
plots[[1]]$plot
```

@@

```{r, fig.cap=paste("Forest Plot for ", plots[[2]]$name," Outcomes"), fig.width=12, fig.height=10}
plots[[2]]$plot
```

@@

```{r, fig.cap=paste("Forest Plot for ", plots[[3]]$name," Outcomes"), fig.width=12, fig.height=10}
plots[[3]]$plot
```

@@

```{r, fig.cap=paste("Forest Plot for ", plots[[4]]$name," Outcomes"), fig.width=12, fig.height=10}
plots[[4]]$plot
```

@@

### Health Behaviour

```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=15}
comparison_plots$`health behaviour`
```

### Physical Health

```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=15}
comparison_plots$`physical health`
```

### Psychology

```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=15}
comparison_plots$psychology
```

### Education

```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=15}
comparison_plots$education
```

>>>>

```{r, fig.cap=paste("Forest Plot for ", plots[[1]]$name," Outcomes"), fig.width=12}
plots[[1]]$plot
```

@@

```{r, fig.cap=paste("Forest Plot for ", plots[[2]]$name," Outcomes"), fig.width=12}
plots[[2]]$plot
```

@@

```{r, fig.cap=paste("Forest Plot for ", plots[[3]]$name," Outcomes"), fig.width=12}
plots[[3]]$plot
```

@@

```{r, fig.cap=paste("Forest Plot for ", plots[[4]]$name," Outcomes"), fig.width=12}
plots[[4]]$plot
```

@@

## Supplementary Forest Plots {.tabset}

```{r, fig.cap=paste("Forest Plot for ", plots[[1]]$name," Outcomes"), fig.width=12}
plots[[1]]$suppplot
```

```{r, fig.cap=paste("Forest Plot for ", plots[[2]]$name," Outcomes"), fig.width=12}
plots[[2]]$suppplot
```

```{r, fig.cap=paste("Forest Plot for ", plots[[3]]$name," Outcomes"), fig.width=12}
plots[[3]]$suppplot
```

```{r, fig.cap=paste("Forest Plot for ", plots[[4]]$name," Outcomes"), fig.width=12}
plots[[4]]$suppplot
```
